Regularising Lotka--Volterra Interaction Matrices by Species Grouping

### 2021-10-24 article.rnw
Add a section to the methods on assessing parsimony.

>>>>

\subsubsection{Assessing parsimony}

To assess the parsimony of each moel, all \num{\Sexpr{numbers::bell(6)^2}} possible models were fitted.
As a measure of parsimony, I selected AIC over BIC on the basis that we want to find the best model for making ecological predictions, rather than seeking the ``true'' \parencite{aho2014model}.
Further, AIC will be more conservative in promoting grouping, as BIC penalises number of parameters more for any reasonably sized data set.
As such, I calculated the AIC for each model.

AIC values can be compared to determine which is the most parsimonious model, but cannot directly be interpreted to find the significance of the difference in parsimony.
As such, I converted the set of AIC values to Akaike weights \parencite{wagenmakers2004aic}.
These give the probability, for each model, that it is the best among the models assessed.
All tests were based upon the relationship between the groupings used in a model and the Akaike weight of the model.

%TODO: Explain the coclassification matrices and the tests.
